### 2023-05-27 paper.tex
new version

\usepackage{booktabs}
\usepackage{multirow}
%
%----------------------------------------------------------------------------------------
%	YOUR CONFIGURATIONS
%----------------------------------------------------------------------------------------
%
\sisetup{math-micro=\text{µ},text-micro=µ}
%
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
\renewcommand{\thefigure}{\arabic{figure}}
%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach in the air}
%
\portugueseTitle{Interferência de Raios e Trovões na Radioatividade: Uma Nova Abordagem no Ar}
%
\author{
  %\authorinfo[ORCID]{NAME}{AFFILIATION},
  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
  \authorinfo[]{Ada Lovelace}{II},
  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
}
%
\affil{ 
  \affiliation{I}{Brown University, USA}
  \affiliation{II}{University of Oxford, UK}
}

\shortHeaderTitle{Interference of Lightning and Thunder on Radioactivity: A Novel Approach ...}
\shortHeaderAuthors{Babbage{\it~et~al.}}
%
\portugueseAbstract{
Este artigo de pesquisa apresenta os resultados de um experimento conduzido por uma equipe de cientistas multidisciplinares, com o objetivo de estudar a interferência de raios e trovões na radioatividade. Utilizando o Electroplumbus nimbodetector, a equipe investigou as complexas interações entre raios, trovões e radioatividade, fornecendo insights fascinantes sobre esse fenômeno intrigante. A equipe coletou dados precisos e quantitativos sobre a intensidade dos raios e os níveis de radioatividade durante tempestades. Essas informações foram analisadas usando o algoritmo Foobar, permitindo a identificação de correlações e padrões. Além disso, a equipe realizou medições comparativas em áreas livres de atividade elétrica, servindo como grupo de controle para comparação de resultados. Essa abordagem meticulosa possibilitou uma análise mais precisa dos efeitos específicos da interferência dos raios na radioatividade. Os resultados obtidos revelam um aumento significativo nos níveis de radioatividade durante a ocorrência de raios e trovões, indicando uma clara influência desses fenômenos atmosféricos. Essa descoberta desafia suposições anteriores e contribui para o avanço do conhecimento sobre os efeitos da atividade elétrica na radioatividade. As implicações dessas descobertas são amplas e podem ter aplicações em várias áreas, incluindo segurança nuclear, proteção ambiental e até mesmo previsão de tempestades e seus efeitos potenciais.
}
%
\portugueseKeywords{raio, radioatividade, experimento aéreo, tempestade}
%
\englishAbstract{
This research paper presents the results of an experiment conducted by a team of multidisciplinary scientists, aimed at studying the interference of lightning and thunder on radioactivity. By utilizing the Electroplumbus nimbodetector, the team investigated the complex interactions between lightning, and radioactivity, providing fascinating insights into this intriguing phenomenon. The team collected accurate and quantitative data on the intensity of lightning, and levels of radioactivity during storms. This information was analyzed using the Foobar algorithm, allowing for the identification of correlations and patterns. Additionally, the team conducted comparative measurements in areas free from electrical activity, serving as a control group for result comparison. This meticulous approach enabled a more precise analysis of the specific effects of lightning interference on radioactivity. The obtained results reveal a significant increase in radioactivity levels during the occurrence of lightning and thunder, indicating a clear influence of these atmospheric phenomena. This discovery challenges previous assumptions and contributes to the advancement of knowledge regarding the effects of electrical activity on radioactivity. The implications of these findings are broad and can have applications in various fields, including nuclear safety, environmental protection, and even storm prediction and its potential effects.
}
%
\englishKeywords{Lightning; Radioactivity; Airborne experiment; Storm}
%
%----------------------------------------------------------------------------------------
\begin{document}

@@

%
\section{Experimental Setup}
\subsection{The 14-Bis flying vehicle}
The 14-Bis flying vehicle, an innovative experimental apparatus, features an open cockpit design that offers an unobstructed view for the driver during ascents into the skies to collect data within lightning storms. The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions.\par
%
Its streamlined shape is optimized for aerodynamic efficiency, minimizing drag and turbulence to facilitate smooth movement through the air. The veicle incorporates pairs of rigid horizontal structures projecting from both sides, designed to provide stability and support during flight \citep{Wipo}, enabling the driver to maintain control even in the presence of strong winds and atmospheric disturbances.\par
%
Within the open cockpit, the driver securely straps into a harness, ready to embark on their mission into lightning storms. The propulsion system powered by the kerosene motor generates the necessary thrust for controlled ascent \citep{Torrens1992}, while the open design ensures an immersive experience for the driver, allowing them to observe and collect data in real-time.\par
%
With its purpose-driven design and reliable motor, the 14-Bis flying vehicle represents an instrumental tool for conducting data collection within lightning storms. The combination of an open cockpit, sturdy structural elements, and efficient propulsion system allows for precise maneuverability and enables researchers to gather valuable insights into the dynamics of these atmospheric phenomena.
%
\begin{figure}[!h]
  \caption{The 14-bis flying vehicle}
  \vspace{-3mm} 
  \begin{center}
    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}
  \end{center}
  {\footnotesize
  Source: Biblioteca Digital Gallica, id btv1b8433366m, Public Domain, availiable on \citep{Beau1907}.\\
  Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons.}
  \label{fig:triangle2}
\end{figure}

@@

Within the experimental setup, a key component is the 4th generation Electroplumbus Nimbodetector, a specialized device designed to collect data from sensors and measure radiation during lightning strikes. The core device of the Nimbodetector is a modified version of the Plumbus Combobulator, carefully adapted to precisely capture and analyze radiation levels at the exact moment of lightning occurrence.

The Electroplumbus Nimbodetector comprises two sensors strategically positioned on the front and rear of the 14-bis flying vehicle. These sensors, with a prism shape, are filled with an enriched Glowing Schleem substance specifically engineered to effectively gather data from lightning discharges. The Schleem material exhibits unique properties that enable accurate measurement of radiation within the immediate vicinity of lightning strikes.

To facilitate data transmission, the sensors are connected to the core device of the Electroplumbus Nimbodetector via electrical wires. This wired connection ensures reliable and swift data transfer, allowing for further analysis of radiation levels associated with lightning activity.

The inclusion of two sensors in the setup serves a crucial purpose: calculating the distance from the lightning source. By analyzing the time difference in data readings between the front and rear sensors, we can accurately estimate the distance traveled by the lightning strike.

\begin{figure}[!h]
  \newcommand\x{0.25}
  \caption{The 4th generation of the Electroplumbus Nimbodetector}
  \begin{center}
    \vspace{-3mm}
		\begin{minipage}[t]{\x\linewidth}
			\includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	
      \captionsetup{justification=centering, font=footnotesize}
			\caption*{(a)}\label{fig:triangle2a}
		\end{minipage}
		\begin{minipage}[t]{\x\linewidth}
			\includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	
      \captionsetup{justification=centering, font=footnotesize}
			\caption*{(b)}\label{fig:triangle2b}
		\end{minipage}\\
  \end{center}%
  \vspace{-1mm}
  {\footnotesize
  Source: Craiyon website, see \citep{Craiyon}\\
  Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance\\
  }
	\label{fig:triangle2}
  \end{figure}\vspace{-9mm}
%
\subsection{Data Collection}

@@

\begin{table}[!h]
\caption{Branzine levels}
\vspace{-5mm}
\footnotesize
\begin{center}
  \begin{tabular}{@{}lccc@{}}
  \toprule
                                         & altitude & \multicolumn{2}{c}{Branzine levels {$[ppm]$}} \\ \cmidrule(l){3-4} 
                                         & {$[m]$}  & on rain             & lack of rain            \\ \midrule
  \multirow{8}{*}{\rotatebox[origin=c]{90}{under the clouds} } 
                                         & $100 \pm 1$      & $0.005 \pm 0.001$   &     $0.006 \pm 0.001$  \\
                                         & $200 \pm 1$      & $1.265 \pm 0.001$   &     $1.260 \pm 0.001$  \\
                                         & $500 \pm 1$      & $40.1  \pm 0.1$    &      $40.2 \pm 0.1$   \\
                                         & $1000\pm 1$      & $392   \pm 5$       &      $395  \pm 5$      \\
                                         & $2000\pm 1$      & $609   \pm 5$       &      $607  \pm 5$      \\
                                         & $3000\pm 1$      & $2709  \pm 10$      &     $2701  \pm 10$     \\
                                         & $4000\pm 1$      & $12701 \pm 10$      &     $12699 \pm 10$     \\
                                         & $5000\pm 1$      & $100831 \pm 10$     &     $100827 \pm 10$    \\ \midrule
  \multirow{7}{*}{\rotatebox[origin=c]{90}{above the clouds} }
                                         & $6000\pm 1$       & $-$                &    $280190 \pm 10$                 \\
                                         & $6200\pm 1$       & $-$                &    $518914 \pm 100$                \\ 
                                         & $6400\pm 1$       & $-$                &    $819827 \pm 100$                \\ 
                                         & $6600\pm 1$       & $-$                &    $100827 \pm 100$                \\ 
                                         & $6800\pm 1$       & $-$                &    $1124225 \pm 1000$              \\ 
                                         & $7000\pm 1$       & $-$                &    $6131823 \pm 1000$              \\ 
                                         & $8000\pm 1$       & $-$                &    $9792921 \pm 1000$              \\ \bottomrule
  \end{tabular}\\[3mm]
\end{center}
Caption: The Branzine levels in relation to altitude, over the Atlantic Ocean (August, 1987).\\
\end{table}
\vspace{-6mm}
Upon analyzing the data, it was observed that there is a increase in Branzine levels with increasing altitude. However, the rise remained below $0.2\%$, indicating an insignificant effect on the Plumbus performance. These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in some conditions such as winter seasons or above the Bermuda's Triangle ($32\%$).

@@

After the evaluation, the collected data in the form of punched tape was sent for analysis. The punched tape contained the recorded information obtained by the Nimbus Detector during the data collection. To process and analyze the data, the Monrobot XI computer was used, employing the Foobar Algorithm programmed in FORTRAN.

\begin{equation}\label{StefanBoltzmannLaw}
  j^{\star}=\sigma\varepsilon T^{4}
\end{equation}
%
\noindent where,
%
\begin{equation}\label{StefanBoltzmannConstant }
  \sigma=5.6704\times10^{-8} Wm^{-2}K^{-4}
\end{equation}

\begin{equation}
  j^{\star}=\sigma\varepsilon T^{4}
\end{equation}

\begin{equation}\label{StefanBoltzmannLaw}
  \begin{split}
    \frac{P}{A}&=j^{\star}=\sigma\varepsilon (T_{v}^{4} - T_{a}^{4}) \\
  \end{split}
\end{equation}

\noindent where,

\begin{equation}\label{StefanBoltzmannLaw}
  \begin{split}
    P = \frac{Q}{t}
  \end{split}
\end{equation}

@@

>>>>

\usepackage{booktabs}
\usepackage{multirow}
%
%----------------------------------------------------------------------------------------
%	YOUR CONFIGURATIONS
%----------------------------------------------------------------------------------------
%
\sisetup{math-micro=\text{µ},text-micro=µ}
%
%----------------------------------------------------------------------------------------
%	YOUR NEW COMMANDS
%----------------------------------------------------------------------------------------
%
\renewcommand{\thefigure}{\arabic{figure}}
%----------------------------------------------------------------------------------------
%	PAPER INFO (for authors)
%----------------------------------------------------------------------------------------
%
\cenSection{Chemistry}
%
\englishTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data Collection and Analysis}
%
\portugueseTitle{Explorando a Dinâmica dos Raios e seus Efeitos Térmicos: Insights a partir da Coleta e Análise de Dados}
%
\author{
  %\authorinfo[ORCID]{NAME}{AFFILIATION},
  \authorinfo[0000-0000-0000-0000]{Charles Babbage}{I},
  \authorinfo[]{Ada Lovelace}{II},
  \authorinfo[0000-0000-0000-0000]{Pierre Curie}{I},
  \authorinfo[0000-0000-0000-0000]{Marie Curie}{},
  \authorinfo[0000-0000-0000-0000]{Grace Hopper}{II},
  \authorinfo[0000-0000-0000-0000]{Santos Dumont}{},
  \authorinfo[]{Nikola Tesla}{},
  \authorinfo[0000-0000-0000-0000]{Galileu Galilei}{I},
  \authorinfo[0000-0000-0000-0000]{Charles Darwin}{I},
  \authorinfo[0000-0000-0000-0000]{Barbara McClintock}{}
}
%
\affil{ 
  \affiliation{I}{Brown University, USA}
  \affiliation{II}{University of Oxford, UK}
}

\shortHeaderTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data ...}
\shortHeaderAuthors{Babbage{\it~et~al.}}
%
\portugueseAbstract{
Os relâmpagos, um fenômeno natural poderoso, não só despertam nossa curiosidade, mas também têm um impacto significativo no ambiente circundante. Este estudo tem como objetivo investigar a dinâmica dos relâmpagos e seus efeitos térmicos por meio de uma análise abrangente de dados coletados pelo Electroplumbus Nimbodetector, em conjunto com o veículo voador 14-Bis. A configuração experimental oferece uma plataforma única para a coleta de dados em tempo real dentro de tempestades de raios, permitindo a exploração dos processos intricados associados às descargas de raios e aos fenômenos térmicos resultantes. A correlação entre a intensidade dos raios e a transferência de radiação térmica é examinada por meio de uma série de experimentos de campo e medições. Os resultados revelam uma relação significativa, com um aumento na energia transferida por radiação correspondendo a raios de maior intensidade. Ao estudar as transições atômicas subjacentes dentro do detector, são obtidos insights sobre a conversão da energia dos relâmpagos em calor no ar circundante. Essas descobertas contribuem para nossa compreensão dos fenômenos térmicos induzidos por relâmpagos e lançam as bases para pesquisas adicionais em ciências atmosféricas, meteorologia e estudos ambientais. As implicações deste estudo se estendem a medidas de segurança aprimoradas, ciência climática e conhecimento aprofundado da dinâmica atmosférica.
}
%
\portugueseKeywords{raio, radioatividade, experimento aéreo, tempestade}
%
\englishAbstract{
Lightning, a powerful natural phenomenon, not only captivates our curiosity but also significantly impacts the surrounding environment. This study aims to investigate the dynamics of lightning and its thermal effects through a comprehensive analysis of data collected by the Electroplumbus Nimbodetector, in conjunction with the 14-Bis flying vehicle. The experimental setup provides a unique platform for real-time data collection within lightning storms, allowing for the exploration of the intricate processes associated with lightning discharges and the resulting thermal phenomena. The correlation between the intensity of lightning strikes and the transfer of thermal radiation is examined through a series of field experiments and measurements. The results reveal a significant relationship, with an increase in the energy transferred by radiation corresponding to higher intensity lightning strikes. By studying the underlying atomic transitions within the detector, insights into the conversion of lightning energy into heat in the surrounding air are gained. These findings contribute to our understanding of lightning-induced thermal phenomena and lay the foundation for further research in atmospheric science, meteorology, and environmental studies. The implications of this study extend to improved safety measures, climate science, and enhanced knowledge of atmospheric dynamics.
}
%
\englishKeywords{Lightning; Radioactivity; Airborne experiment; Storm}
%
%----------------------------------------------------------------------------------------
\begin{document}

@@

\section{Introduction}
%
Lightning, a powerful natural phenomenon, has long fascinated scientists and researchers due to its immense energy and unpredictable behavior. The study of lightning and its effects on the surrounding environment is crucial for gaining a deeper understanding of atmospheric dynamics and improving safety measures against its potential hazards. In particular, the transfer of thermal radiation during lightning strikes plays a significant role in shaping the thermal characteristics of the atmosphere and has far-reaching implications for meteorology, climate science, and environmental studies.\par
%
To investigate the dynamics of lightning and its thermal effects, advanced experimental apparatus and specialized devices are required. In this paper, we present the results of a comprehensive study conducted using the 14-Bis flying vehicle and the Electroplumbus Nimbodetector, designed specifically for data collection within lightning storms. These innovative instruments enable researchers to gather valuable insights into the intricate processes associated with lightning discharges and the resulting thermal phenomena.\par
%
In the following sections, we present the experimental setup, data collection methods, and data analysis techniques employed in this study. Subsequently, we discuss the results obtained, highlighting the correlation between lightning strikes and the transfer of thermal radiation. Finally, we conclude with a summary of the findings, their significance, and future research directions.\par
%
\section{Experimental Setup}
\subsection{The 14-Bis flying vehicle}
The 14-Bis flying vehicle, an innovative experimental apparatus, features an open cockpit design that offers an unobstructed view for the driver during ascents into the skies to collect data within lightning storms. The vehicle is equipped with a two clicle kerosene fueled motor \citep{Torrens1992} that drives a large propeller, providing efficient propulsion for navigating through turbulent atmospheric conditions.\par
%
Its streamlined shape is optimized for aerodynamic efficiency, minimizing drag and turbulence to facilitate smooth movement through the air. The veicle incorporates pairs of rigid horizontal structures projecting from both sides, designed to provide stability and support during flight \citep{Wipo}, enabling the driver to maintain control even in the presence of strong winds and atmospheric disturbances.\par
%
Within the open cockpit, the driver securely straps into a harness, ready to embark on their mission into lightning storms. The propulsion system powered by the kerosene motor generates the necessary thrust for controlled ascent \citep{Torrens1992}, while the open design ensures an immersive experience for the driver, allowing them to observe and collect data in real-time.\par
%
With its purpose-driven design and reliable motor, the 14-Bis flying vehicle represents an instrumental tool for conducting data collection within lightning storms. The combination of an open cockpit, sturdy structural elements, and efficient propulsion system allows for precise maneuverability and enables researchers to gather valuable insights into the dynamics of these atmospheric phenomena.
%
\begin{figure}[!h]
  \caption{The 14-bis flying vehicle}
  \vspace{-3mm} 
  \begin{center}
    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}
  \end{center}
  {\footnotesize
  Source: Biblioteca Digital Gallica, id btv1b8433366m, Public Domain, availiable on \citep{Beau1907}.\\
  Caption: The 14-bis in its final form, with octagonal-planform interplane ailerons.}
    \label{fig:triangle2}
  \end{figure}

@@

  The 4th generation Electroplumbus Nimbodetector is a specialized device designed to collect data from a sensor and measure thermal radiation during lightning strikes. The device incorporates a modified version of the Plumbus Combobulator in its core, along with a specially engineered sensor that has a prism shape and is filled with an enriched Glowing Schleem substance. The purpose of the device is to gather data on lightning discharges and study their effects on the surrounding air.\par
  %
  The sensor within the Electroplumbus Nimbodetector is designed to capture thermal radiation emitted during lightning strikes. When a lightning event occurs, the Glowing Schleem inside the prism-shaped sensor heats up. Due to the low heat capacity of the Schleem, the temperature rise is rapidly measured, providing instant data on the thermal effects of the lightning discharge.\par
  %
  To determine the temperature of the air surrounding the sensor, the Plumbus Combobulator within the device incorporates a conventional thermometer with hight heat capaciity. The thermometer is strategically strategically positioned on the rear of the 14-bis flying vehicle to measure the air temperature in the vicinity of the sensor. By comparing the temperature of the Schleem-filled sensor and the air temperature measured by the thermometer, we can establish the temperature difference, which is crucial in assessing the impact of the lightning strikes' radiation on the surrounding air.\par
  %
  The Electroplumbus Nimbodetector undergoes rigorous calibration and validation processes to ensure accurate and reliable measurements. Prior to deployment, the device is calibrated against reference instruments and tested under controlled laboratory conditions to establish its performance characteristics. Special attention is given to the sensitivity, precision, and response time of the sensor and thermometer to ensure the accurate capture of data during lightning strikes.
  %
  \begin{figure}[!h]
    \newcommand\x{0.25}
    \caption{The 4th generation of the Electroplumbus Nimbodetector}
    \begin{center}
      \vspace{-3mm}
      \begin{minipage}[t]{\x\linewidth}
        \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	
        \captionsetup{justification=centering, font=footnotesize}
        \caption*{(a)}\label{fig:triangle2a}
      \end{minipage}
      \begin{minipage}[t]{\x\linewidth}
        \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	
        \captionsetup{justification=centering, font=footnotesize}
        \caption*{(b)}\label{fig:triangle2b}
      \end{minipage}\\
    \end{center}%
    \vspace{-1mm}
    {\footnotesize
    Source: Craiyon website, see \citep{Craiyon}\\
    Caption: The (a) figure displays the core of the device with the Plumbus Combobulator inside and (b) shows the lightning detector filled by enriched Glowing Schleem substance\\
    }
    \label{fig:triangle2}
    \end{figure}\vspace{-4mm}
  %
  \subsection{Data Collection}

@@

  \begin{table}[!h]
  \caption{Branzine levels}
  \vspace{-5mm}
  \footnotesize
  \begin{center}
    \begin{tabular}{@{}lccc@{}}
    \toprule
                                           & altitude & \multicolumn{2}{c}{Branzine levels {$[ppm]$}} \\ \cmidrule(l){3-4} 
                                           & {$[m]$}  & on rain             & lack of rain            \\ \midrule
    \multirow{8}{*}{\rotatebox[origin=c]{90}{under the clouds} } 
                                           & $100 \pm 1$      & $0.005 \pm 0.001$   &     $0.006 \pm 0.001$  \\
                                           & $200 \pm 1$      & $1.265 \pm 0.001$   &     $1.260 \pm 0.001$  \\
                                           & $500 \pm 1$      & $40.1  \pm 0.1$    &      $40.2 \pm 0.1$   \\
                                           & $1000\pm 1$      & $392   \pm 5$       &      $395  \pm 5$      \\
                                           & $2000\pm 1$      & $609   \pm 5$       &      $607  \pm 5$      \\
                                           & $3000\pm 1$      & $2709  \pm 10$      &     $2701  \pm 10$     \\
                                           & $4000\pm 1$      & $12701 \pm 10$      &     $12699 \pm 10$     \\
                                           & $5000\pm 1$      & $100831 \pm 10$     &     $100827 \pm 10$    \\ \midrule
    \multirow{7}{*}{\rotatebox[origin=c]{90}{above the clouds} }
                                           & $6000\pm 1$       & $-$                &    $280190 \pm 10$                 \\
                                           & $6200\pm 1$       & $-$                &    $518914 \pm 100$                \\ 
                                           & $6400\pm 1$       & $-$                &    $819827 \pm 100$                \\ 
                                           & $6600\pm 1$       & $-$                &    $100827 \pm 100$                \\ 
                                           & $6800\pm 1$       & $-$                &    $1124225 \pm 1000$              \\ 
                                           & $7000\pm 1$       & $-$                &    $6131823 \pm 1000$              \\ 
                                           & $8000\pm 1$       & $-$                &    $9792921 \pm 1000$              \\ \bottomrule
    \end{tabular}\\[3mm]
  \end{center}
  Caption: The Branzine levels in relation to altitude, over the Atlantic Ocean (August, 1987).\\
  \end{table}
  \vspace{-6mm}
  Upon analyzing the data, it was observed that there is a increase in Branzine levels with increasing altitude. However, the rise remained below $0.2\%$, indicating an insignificant effect on the Plumbus performance. These findings align with prior research \citep{Gagaia1923}, which suggests that Branzine levels typically exhibit a notable increase of over $5\%$ in some conditions such as winter seasons or above the Devil's Triangle ($32\%$).

@@

  After the evaluation, the collected data in the form of punched tape was sent for analysis. The punched tape contained the recorded information obtained by the Nimbus Detector during the data collection. To process and analyze the data, the Monrobot XI computer was used, employing the Foobar Algorithm programmed in FORTRAN. The behavior of the sensor can be described by the Stefan-Boltzmann law, which relates the energy radiated by a black body to its temperature.

According to the Stefan-Boltzmann law, the power radiated by a gray body is proportional to the fourth power of its absolute temperature $T$ and can be expressed as:

\begin{equation}\label{StefanBoltzmannLaw}
  j^{\star}=\sigma T^{4}
\end{equation}
%
\noindent where $j^{\star}$ represents the black-body radiant emittance, and $\sigma$ is the Stefan-Boltzmann constant ($\sigma=5.6704\times10^{-8} Wm^{-2}K^{-4}$).
%
To calculate the heat transfer rate by radiation (almost entire in the infrared spectrum band), we modify the previous equation by incorporating the emissivity $\varepsilon$ of the sensor, to make the sensor behave like a gray body. The modified equation is as follows:

\begin{equation}
  \frac{Q}{t}=A\sigma\varepsilon (T_{v}^{4} - T_{a}^{4})
\end{equation}
%
Here, $Q \slash t$ represents the radiationheat transfer rate, taking into account the emissivity of the sensor $\varepsilon$ . The emissivity is a dimensionless quantity that varies between $0$ and $1$, where $0$ represents a perfectly reflective surface (no radiation emitted) and $1$ represents a perfectly black body (maximum radiation emitted). In this case, the manufacturer's manual establishes the value $\varepsilon = 0.998$. Also, $A$ is the surface sensor's area ($A=\SI{128.34}{\milli\meter^2}$).

\section{Results}

The analysis of data collected by the Electroplumbus Nimbodetector reveals a significant correlation between the intensity of lightning strikes and the transfer of thermal radiation. Through a series of field experiments and measurements, we observed a consistent increase in the energy transferred by radiation during lightning events.

@@

The chart presented in Figure 1 illustrates the relationship between the intensity of lightning strikes and the corresponding heat transfer rate by radiation. As the intensity of the lightning strike increases, there is a clear upward trend in the energy transferred. This observation supports the hypothesis that lightning strikes contribute to an enhanced transfer of thermal radiation to the surrounding air.

The strong correlation observed between lightning strikes and the energy transferred by radiation reinforces the reliability of the data collected by the Electroplumbus Nimbodetector. These findings provide valuable insights into the thermal dynamics associated with lightning discharges and contribute to a better understanding of the effects of lightning on the surrounding environment.

Moreover, it is important to note that light alone cannot directly heat gas molecules. Instead, during a lightning strike, the light emitted excites the electrons in atoms within the detector. These atoms are already vibrating at a certain frequency. Some of these atoms vibrate with sufficient vigor that their vibrational energy matches the electronic energy (photons) absorbed from the lightning, effectively reaching resonance with the solar energy. As a result, these atoms undergo a quantum transition from being "electronically excited" to "vibrationally excited," causing the entire atom to move. The surrounding air perceives this excited vibration as "heat."

This mechanism provides a deeper understanding of how the energy from a lightning strike is converted into thermal energy in the air. By studying the vibrational and electronic transitions occurring within the atoms of the detector, we can further elucidate the intricate processes involved in the thermal effects of lightning discharges.

In conclusion, this study demonstrates a strong correlation between the intensity of lightning strikes and the transfer of thermal radiation. The data collected by the Electroplumbus Nimbodetector, along with the presented chart, provides robust evidence supporting this relationship. Additionally, the exploration of the underlying processes involving electronic and vibrational transitions within the detector atoms enhances our comprehension of how lightning energy is converted into heat in the surrounding air. These findings contribute to the scientific understanding of lightning-induced thermal phenomena and lay the foundation for future research in this field.
